### 2019-05-28 doc/leader/frontpage_with_picture.tex
added comment

\begin{textblock}{150}(28,225)
\fontsize{10pt}{17pt}\selectfont
\begin{tabbing}
xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Degree course:	\> Computer Science	\\		% insert name of degree course
Authors:		\> Anna Doukmak, Ramon Boss		\\					% insert names
Tutor:	\> Kai Brünnler @TODO Dr.?		\\							% insert names
%Constituent:	\> [Wwwww AG]					\\							% insert names
Experts:		\> Urs Keller				\\							% insert names
Date:			\> \versiondate					\\							% read from file leader/version.tex
\end{tabbing}

>>>>

\begin{textblock}{150}(28,225)
\fontsize{10pt}{17pt}\selectfont
\begin{tabbing}
xxxxxxxxxxxxxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx \kill
Degree course:	\> Computer Science	\\		% insert name of degree course
Authors:		\> Anna Doukmak, Ramon Boss		\\					% insert names
Tutor:	\> Kai Brünnler // TODO Dr.?		\\							% insert names
%Constituent:	\> [Wwwww AG]					\\							% insert names
Experts:		\> Urs Keller // TODO remove?				\\							% insert names
Date:			\> \versiondate					\\							% read from file leader/version.tex
\end{tabbing}
